The French Covid-19 vaccination policy did not solve vaccination inequities: a nationwide longitudinal study on 64.5 million individuals

### 2022-07-05 ms/figs.Rmd
add description labels

# Save as csv
write.csv(supptab, file = "../ms/SuppTable_OR_wide.csv", row.names = FALSE)

>>>>

# Add full text of the labels
txt <- read.csv("../data/insee_labels_en.csv", sep = ";")
names(txt) <- c("predictor", "description", "unit")
# Remove "X" at start of name
iX <- which(substr(txt$predictor, 1, 1) == "X") # Lines with "X"
txt[iX, "predictor"] <- vapply(txt[iX, "predictor"], FUN = function(x) substr(x, 2, nchar(x)), FUN.VALUE = "x") # Remove "X" on these lines

# Check that we have all labels
all(is.element(supptab$predictor, txt$predictor))

stb <- merge(supptab, txt, by = "predictor", all.x = TRUE)
stb

# Save as csv
write.csv(stb, file = "../ms/SuppTable_OR_wide.csv", row.names = FALSE)
